\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-30 paper.tex
working on version control section

Tickets to enter Kinkaku-ji are long sheets of printed paper with calligraphy.
The tickets are large and visually appealing; they are souvenirs unto themselves
that one might feel inclined to keep around. Over the course of our three month
stay we visited Kinkaku-ji multiple times. For each visit, we received identical
tickets. Seemingly, the design on the tickets do not change on a regular basis,
if at all.

@@

Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
but still covered all of the uses for our app at the time. The top of the screen
had two dropdown menus. The one on the left (which is open shown open in
Figure~\ref{fig:oldUI}) shows AR image targets in the area that users could
look for and scan. The right dropdown would be dynamically populated in each
region with buttons bearing different images. These images were ones that
Atticus wanted to be viewable in AR using ground plane detection. When tapped,
each button would create a 3D Cube, with the given image on each face, and place
it on the ground where the user was pointing. 
%TODO provide a figure of the AR cube

@@

@@

>>>>

Tickets to enter Kinkaku-ji are long sheets of printed paper with calligraphy.
The tickets are large and visually appealing; they are souvenirs unto themselves
that one might feel inclined to keep around. Over the course of our three month
stay we visited Kinkaku-ji multiple times. For each visit, we received identical
tickets. Seemingly, the design on the tickets do not change on a regular basis,
if at all. Figure~\ref{fig:kinkakujiTicket} shows a ticket we kept from one of
our visits to Kinkaku-ji.

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{kinkakuji-ticket.jpeg}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:kinkakujiTicket}
\end{figure}

@@

Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
but still covered all of the uses for our app at the time. The top of the screen
had two dropdown menus. The one on the left (which is open shown open in
Figure~\ref{fig:oldUI}) shows AR image targets in the area that users could
look for and scan. The right dropdown would be dynamically populated in each
region with buttons bearing different images. These images were ones that
Atticus wanted to be viewable in AR using ground plane detection. When tapped,
each button would create a 3D Cube, with the given image on each face, and place
it on the ground where the user was pointing. Figure~\ref{fig:floatingCube}
shows this feature in action.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{floating-cube.png}
	\caption{An ``art cube'' floating over the water containing a placeholder
    programming meme}
	\label{fig:floatingCube}
\end{figure}

@@

% TODO this whole section should probabyl be in the appendix
\section{Version Control}
\label{sec:versionControl}

Over the course of the project, we had to develop multiple applications in
different languages. In total, we opened five different repositories: the blog,
the \LaTeX source code for our paper, the Arduino code for the heart project,
and of course one for Editour and another for ARuko. These five repositories
span across multiple different markup and programming languages, including C\#,
C++, JavaScript, HTML, CSS (and the \LaTeX markup language used to typeset this
paper.) This gave us a welcome amount of practice using git for version control,
as well as GitHub's other features oriented around coordinating a team.

All three members of the team were contributing code and updating assets such as
graphics and sound. Code complexity grew quickly as more features were added
across the entire software stack. Git and GitHub enabled us to view the history
of the code and revert back to working versions when absolutely necessary. We
researched the proper methodology of using version control in a small team,
applying this methodology as best we could. This enabled us to work together
efficiently, track down bugs, undo mistakes, and sometimes review each other's
code for quality when time allowed.

@@

\subsection{GitHub Tools}
\label{sec:gitHubTools}

Some members of our team were very excited by the workflows GitHub's tools
enabled.

Initially, we experimented with using a four-column Kanban board to keep track
of our progress. Figure~\ref{fig:kanbanBoard} shows a screenshot of this page on
GitHub.

The Kanban technique stems from Toyota in the 1940s. Kanban means ``visual
signal'' or ``card'' in Japanese, which describes the core component of the
technique~\autocite{terry2019}. At Toyota, line-workers would move colored cards
to notify other teams that parts needed for assembly work were in short supply.
Now, Kanban boards are integral to Agile software development. Still, some teams
use physical Kanban boards, often using sticky notes and whiteboards.

The advantage of using a Kanban board is that each feature or bug that
is being worked on can be assigned directly to a collaborator on the project. It
is then that person's responsibility to work on those tasks and update the
status of those tasks on the board. We abandoned this when moving onto the main
project because we came to realize that this structure was not necessary---there
were only three members on the team, and we were almost always in the same room
when working on the project. For Editour, we tracked features and issues using
the Issues page instead, which is discussed in
Section~\ref{sec:editourFrontendTesting}.

Creating ``pull requests'' through the GitHub web interface has a few advantages
over directly merging code using git. Firstly, the pull request feature
integrates with ``Issues'' page very well. By typing `resolves' along with the
number associated with an issue into the description of a pull request, GitHub
will automatically close the issue when the pull request is approved. This is
not only remarkably convenient, but also self-documenting since the descriptions
of pull requests would contain the issues they were resolving. Secondly,
creating a pull request allows code to be reviewed by other members of the team
very easily. Reviewers can view the entire diff and add comments line-by-line.
Other collaborators can easily respond to those comments. Reviewers can also
request certain features be changed before the branch is merged, which allowed
us to enforce that issues with the code were actually addressed.
% TODO explain what the heck a diff is

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kanban-board.png}
	\caption{A screenshot of the Kanban board we used for developing our
    biweekly blog}
	\label{fig:kanbanBoard}
\end{figure}
